Understanding domestic abuse

### 2019-07-23 JeS_fields.tex
Impact summary update

Our insights about police mis-recording of domestic abuse will improve the experiences of victims in the CJS, increase trust, and willingness to report future incidents.

>>>>

For charities and the government, insights from our research (risk factors of ) will provide useful information for the most effective targeting (geographical and temporal) of domestic abuse awareness campaigns.

 will benefit from a comprehensive investigation of a wide range of risk factors of domestic abuse victimisation.

Our insights about police mis-recording of domestic abuse will improve the experiences of victims in the CJS, increase their trust, and willingness to report future incidents. The police will also benefit from a deeper understanding of the factors governing reporting behaviour, its temporal characteristics throughout the year, and this knowledge will allow for an improved allocation of scarce police resources. Our research on the predictors of serious harm will help design better interventions.
